A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-15 manuscript.Rmd
clarifications and typos in README
extend mentioning of singularity closes #30

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components central to a reproducible workflow: version control (git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). "}
knitr::include_graphics("Images/nutshell.svg", auto_pdf = TRUE)
```

@@

>>>>

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components central to a reproducible workflow: version control (git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). "}
knitr::include_graphics("Images/placeholder.png")
```

@@

This flexibility to fully control the software environment is of particular interest for software infrastructures where the user cannot install software themself, because of limited rights e.g. on cloud computing platforms or High-Performance Computing Clusters. However, executing docker itself needs special rights which are seldomly granted on High-Performance Computing Cluster. For this case, Singularity provides a fully compatible alternative (see Section under [Linux]).
